Predictors of frog survival following translocations - primary analyses

### 2023-05-18 code/translocation_survival_analysis.Rmd
Remove unnecessary comments

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>%
  ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order)
      geom_linerange(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.5, position = position_dodge2(width=0.5)) +
      geom_point(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor), size = 3, position = position_dodge2(width=0.5)) + 
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", linewidth = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

@@

-   Strong effect of site/translocation on frog survival.
-   Survival is highly variable across sites, but relatively invariant within a site.
-   Indicates need to include site_id and/or translocation_id as group-level effect(s).

@@

# Confirm our prior is flat
prior_summary(m1_flat)

@@

predictions_m1d <- posterior_epred(m1d_reduce, newdata = m1d_group_means)
# predictions_m1d <- posterior_predict(m1d_reduce, newdata = m1d_group_means) # original code that produced incorrect uncertainty estimates

>>>>

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>%
  ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order
      geom_linerange(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.5, position = position_dodge2(width=0.5)) +
      geom_point(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor), size = 3, position = position_dodge2(width=0.5)) + 
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", linewidth = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

@@

-   Strong effect of site/translocation on frog survival.
-   Survival is highly variable across sites, but relatively constant within a site.
-   Indicates need to include site_id and/or translocation_id as group-level effect(s).

@@

# Confirm that prior is flat
prior_summary(m1_flat)

@@

predictions_m1d <- posterior_epred(m1d_reduce, newdata = m1d_group_means)
